Verifying Demonstrations

### 2017-09-27 SystemModel.tex
Removes questions that have moved to issues or no longer relevant

The protests described above can be captured using this definition by splitting 
them up into subprotests.
Each subprotest will then be captured by our definition and to find the total 
we can just sum up the results.

\begin{frame}
\begin{question}
  With this definition, can we participate in two sub-protests and be counted 
  twice?
\end{question}
\begin{remark}
  Perhaps not if linkability is tied to the cause.
\end{remark}
\end{frame}
\begin{remark}
  This sort of depends on the unique ring/list signature scheme that we use.
  As long as we can provide linkability between a user's proofs, we can consider 
  it the same protest.
  When we cannot, it must be a new protest.
  So this is supposedly decided by the one setting up the unique ring/list 
  signature scheme --- which we do not know yet how it will be done.
\end{remark}

>>>>

The protests described above can be captured using this definition by splitting 
them up into subprotests.
Each subprotest will then be captured by our definition and to find the total 
we can just sum up the results.
The same for marches, the marching path can be divided into subprotests with 
coarse coordinates that slightly overlap.

### 2017-09-27 properties.tex
Removes questions that have moved to issues or no longer relevant

\begin{question}
  How hard is it to reuse old proofs?
  Forge all signatures due to changed values?
\end{question}

@@

\begin{question}
  Why should anyone trust these witnesses?
  What are the assumptions?
  Signed over a short period of time?\footnote{%
    In a sense, if they collude they have shown support for the cause.
    As long as they are not Sybil it should be fine?
  }
\end{question}

@@

\begin{question}
  Trusted party for the group signatures?
\end{question}
\begin{question}
  How can we do \acp{LP} with 1000s of witnesses each?
  Can we do some preprocessing?
  Ad-hoc networks, broadcast \acp{LP}?
\end{question}
\begin{question}
  Must tie credentials to something unique: phone, phone subscription?
  Cannot register twice, government control?
\end{question}

\begin{question}
  What if Alice acts as a witness for Eve's agents?
  Can that violate her privacy?
\end{question}
\begin{question}
  What if Eve's agents act as witnesses?
  Can they track their signatures to track users?
  Can Alice detect if this happens?
\end{question}

@@

If the proofs are stored publicly, then an individual can check that their 
proof has been included (committed) there.
Thus \cref{IndividualVerif} is fulfilled.
Similarly for universal verifiability.
If the storage is public, then anyone can download all the proofs, verify their 
eligibility and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
To have any verifiability, we need the storage to be immutable --- i.e.\ it 
prevents malicious changes.

>>>>

@@

@@

@@

If the proofs are stored publicly, then an individual can check that their 
proof has been included (committed) there.
Thus \cref{IndividualVerif} is fulfilled.
Similarly for universal verifiability.
If the storage is public, then anyone can download all the proofs, verify their 
eligibility and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
